\documentclass[11pt, a4paper]{awesome-cv}
\input{preamble.tex}

\name{Shangwei}{GUO}
\position{Research Fellow}
\address{Room No.B2c 06 , Block N4, School of Computer Science and Engineering, Nanyang Technological University, Singapore}
\googlescholar{wQrVkBYAAAAJN}{Shangwei GUO} % chktex 8
\email{shangwei.guo@ntu.edu.sg}
\homepage{www.swguo.com}

\begin{document}

\makecvheader%

\makecvfooter{\today}{Shangwei GUO~~~·~~~Curriculum Vitae}{\thepage}

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Biography}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}
	Shangwei GUO is a research fellow at Cyber Security Lab, School of Computer Science and Engineering, Nanyang Techological University (NTU). His supervisor is Prof. Yang LIU. Before joining NTU, he worked at the Database Lab, Hong Kong Baptist University as a postdoctoral research fellow (supervised by Prof. Jianliang XU). He obtained his PhD degree from the School of Computer Science, Chongqing University (supervised by Prof. Tao XIANG). 
	
	\indent His research interests include
	\vspace{0.2cm}
	{
		\begin{cvitems}
			\item{Secure Deep Learning}
			\item{Verifiable Query Processing}
			\item{Cloud Security and Data Privacy}
		\end{cvitems}
	}
\end{cvparagraph}

% \vspace{-0.2cm}
\cvsection{Education}
\begin{cventries}
    \cventry%
    {Ph.D. in Computer Science and Technology}
    {Chongqing University}
    {Chongqing, China}
    {Feb. 2014 - Dec. 2017} % chktex 8
    {}
    \vspace{-0.3cm}
	\cventry%
	{Study in Applied Mathematics}
	{Chongqing University}
	{Chongqing, China}
	{Sep. 2012 - Jan. 2014} % chktex 8
	{}
	\vspace{-0.3cm}
    \cventry%
    {B.S. in Mathematics}
    {Henan Normal University}
    {Xinxiang, China}
    {Sep. 2008 - Jun. 2012} % chktex 8
    {}
    \vspace{-0.3cm}
\end{cventries}

\vspace{-0.2cm}
\cvsection{Professional Experience}
\begin{cventries}
    \cventry%
    {Postdoctoral Research Fellow}
    {Nanyang Technological University}
    {Singapore}
    {Apr. 2019 - Now} % chktex 8
    {
        \begin{cvitems}
            \item{Supervisor: Prof.\ Yang LIU}
            \item{Research Direction: Secure Distributed Deep Learning}
        \end{cvitems}
    }
    \cventry%
    {Postdoctoral Research Fellow}
    {Hong Kong Baptist University}
    {Hong Kong}
    {Jan. 2018 - Apr. 2019} % chktex 8
    {
        \begin{cvitems}
            \item{Supervisor: Prof.\ Jianliang XU}
            \item{Research Direction: Verifiable Outsourcing Query Processing}
        \end{cvitems}
    }
	\cventry%
	{Ph.D. Candidate}
	{Chongqing University}
	{Chongqing}
	{Feb. 2014 - Dec. 2017} % chktex 8
	{
		\begin{cvitems}
			\item{Supervisor: Prof.\ Tao XIANG}
			\item{Thesis: Research on Visual Security Index}
		\end{cvitems}
	}
\end{cventries}

% \vspace{-0.2cm}
\cvsection{Publications}
\begin{cvparagraph}
    \nocite{*}
    \printbibliography[heading=none]
\end{cvparagraph}

\newpage
\cvsection{Awards}
\begin{cvawards}
    \cvaward{National Scholarship for Doctoral Candidates}{Ministry of Education of China}{2016} % chktex 8
\end{cvawards}

\cvsection{Talks}
\begin{description}
    \item[\honordatestyle{1}] \honortitlestyle{vCBIR: A Verifiable Search Engine for Content-based Image Retrieval, 36th IEEE International Conference on Data Engineering, Texas, USA, 2020 (online).}
    \item[\honordatestyle{2}] \honortitlestyle{ImageProof: Enabling Authentication for Large-Scale Image Retrieval, 35th IEEE International Conference on Data Engineering,Macau, China, 2019.}
    \item[\honordatestyle{3}] \honortitlestyle{Perceptual Visual Security Index Based on Edge and Texture Similarities, 3th CACR International Conference on Chaotic Communication Security, Shandong, China, 2017.}
\end{description}

\cvsection{Service}
\begin{cvskills}
    \cvskill{Guest Editor}{Multimedia Tools and Applications, Special Issue on Blockchain-based Multimedia Security}
    \cvskill{}{Signal Processing: Image Communication, Special Issue on Multimedia Big Data Privacy and Processing Based on Compressive Sensing}
    \cvskill{}{Measurement, Special Issue on Advanced Signal Processing for Internet of Medical Things}
    \cvskill{PC Member}{International Workshop on Mobile Ubiquitous Systems and Technologies (MUST2020)}
    \cvskill{Review}{IEEE Transactions on Knowledge and Data Engineering}
    \cvskill{}{IEEE Transactions on Circuits and Systems for Video Technology}
    \cvskill{}{ACM Transactions on Internet Technology}
    \cvskill{}{Neural Networks}
    \cvskill{}{ EURASIP Journal on Advances in Signal Processing}
\end{cvskills}

\end{document}